Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-02-08 WSSSPE4_report/survey_details.tex
remaining formatting fixes for survey appendix

\noindent {\bf 1. Please indicate how strongly you agree or disagree with the following statements}

@@

\begin{figure}[!htb]
    \begin{subfigure}{0.34\textwidth}
    \includegraphics[width=\linewidth]{figures/SurveyFig1rev}
    \caption{The plenary sessions had a good mix of topics and speakers.}
    \label{fig:SFig1}
    \end{subfigure}
    ~
    \begin{subfigure}{0.32\textwidth}
    \includegraphics[width=\linewidth]{figures/SurveyFig2rev}
    \caption{The balance was right between talks, panels, and lightning talks.}
    \label{fig:SFig2}
    \end{subfigure}
    \begin{subfigure}{0.25\textwidth}
    \includegraphics[width=\linewidth]{figures/SurveyFig3rev}
    \caption{There was sufficient time for discussion.}
    \label{fig:SFig3}
    \end{subfigure}
    \caption{Responses to generate questions about the conference program}
\end{figure}

\noindent {\bf 2. What part of the meeting was the most valuable? select all that apply}

\todo{move table and figure to be in a single row}

\begin{table}[h!]
\rowcolors{1}{}{lightgray}
\centering
\caption{Value of meeting parts}
\label{tab:survey_parts}
\begin{tabular}{|l|c|}
\hline
{\bf Answer} &
{\bf Count} \\ \hline
Plenary &
19 \\
Panel &
14 \\
Working Groups &
36 \\
Other &
5 \\
Total &
74 \\
\hline
\end{tabular}
\end{table}

\begin{figure}[h!]
\includegraphics[width=0.4\textwidth]{figures/SurveyFig4rev}
\caption{What part of the meeting was the most valuable?
\label{fig:SFig4}}
\end{figure}

\noindent {\bf 3. What additional topics would you like to see discussed at the next meeting?}

@@

\noindent {\bf 4. What could be improved?}

@@

\noindent {\bf 5. What would make you more likely to invest time in future WSSSPE initiatives?}

@@

\noindent {\bf 6. Would you be interested in joining a professional society focused around the topics of WSSSPE?}

\todo{move table and figure to be in a single row}

\begin{table}[h!]
\centering
\caption{A WSSSPE society?}
\label{tab:survey_society}
\begin{tabular}{|l|c|}
\hline
{\bf Answer} &
{\bf Count} \\ \hline
Yes &
24 \\
No &
3 \\
Maybe &
18 \\
Total &
45 \\
\hline
\end{tabular}
\end{table}

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{figures/SurveyFig5rev}
\caption{Would you be interested in joining a professional society focused around the topics of WSSSPE?
\label{fig:SFig5}}
\end{figure}

\noindent {\bf 7. Will you be part of a working group  with colleagues going forward  on a topic addressed at WSSSPE, and if so, which one?}

\todo{move table and figure to be in a single row}

\begin{table}[h!]
\centering
\caption{Continuing working groups?}
\label{tab:survey_continuing_wgs}
\begin{tabular}{|l|c|}
\hline
{\bf Answer} &
{\bf Count} \\ \hline
Yes &
32 \\
No &
4 \\
Maybe &
9 \\
Total &
45 \\
\hline
\end{tabular}
\end{table}

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{figures/SurveyFig6rev}
\caption{Will you be part of a working group  with colleagues going forward  on a topic addressed at WSSSPE?
\label{fig:SFig6}}
\end{figure}

\noindent {\bf 8. Working Group Name}

@@

\noindent {\bf 9. Do you have any other comments or suggestions or ideas?}

>>>>

\noindent \textbf{1. Please indicate how strongly you agree or disagree with the following statements}

@@

\begin{figure}[!htb]
    \captionsetup[subfigure]{position=b}
    \centering
    \subcaptionbox{
    The plenary sessions had a good mix of topics and speakers.
    \label{fig:SFig1}
    }{\includegraphics[width=.34\linewidth]{figures/SurveyFig1rev}}
    ~
    \subcaptionbox{
    The balance was right between talks, panels, and lightning talks.
    \label{fig:SFig2}
    }{\includegraphics[width=.32\linewidth]{figures/SurveyFig2rev}}
    ~
    \subcaptionbox{
    There was sufficient time for discussion.
    \label{fig:SFig3}
    }{\includegraphics[width=.25\linewidth]{figures/SurveyFig3rev}}
    \caption{Responses to generate questions about the conference program}
\end{figure}

\noindent \textbf{2. What part of the meeting was the most valuable? select all that apply}

\begin{figure}[h!]
    \CenterFloatBoxes
    \begin{floatrow}
    \ffigbox[\FBwidth]{%
        \includegraphics[width=0.35\textwidth]{figures/SurveyFig4rev}%
    }{%
        \captionsetup{width=\linewidth}
        \caption{What part of the meeting was the most valuable?
        \label{fig:SFig4}}%
    }
    \hfill
    \killfloatstyle\capbtabbox[\linewidth]{%
    \rowcolors{1}{}{lightgray}
    \begin{tabular}{@{}ll@{}}
    \toprule
    Answer & Count \\
    \midrule
    Plenary & 19 \\
    Panel & 14 \\
    Working Groups & 36 \\
    Other & 5 \\
    Total & 74 \\
    \bottomrule
    \end{tabular}
    }{%
        \caption{Value of meeting parts}%
    }
    \end{floatrow}
\end{figure}

\noindent \textbf{3. What additional topics would you like to see discussed at the next meeting?}

@@

\noindent \textbf{4. What could be improved?}

@@

\noindent \textbf{5. What would make you more likely to invest time in future WSSSPE initiatives?}

@@

\noindent \textbf{6. Would you be interested in joining a professional society focused around the topics of WSSSPE?}

\begin{figure}[h!]
    \CenterFloatBoxes
    \centering
    \begin{floatrow}
    \ffigbox[\FBwidth]{%
        \includegraphics[width=0.35\textwidth]{figures/SurveyFig5rev}%
    }{%
        \captionsetup{width=\linewidth}
        \caption{Would you be interested in joining a professional society
        focused around the topics of WSSSPE?
        \label{fig:SFig5}}%
    }
    %\hfill
    ~
    \killfloatstyle\capbtabbox[\linewidth]{%
    \rowcolors{1}{}{lightgray}
    \begin{tabular}{@{}ll@{}}
    \toprule
    Answer & Count \\
    \midrule
    Yes & 24 \\
    No & 3 \\
    Maybe & 18 \\
    Total & 45 \\
    \bottomrule
    \end{tabular}
    }{%
        \caption{A WSSSPE society?}%
        \label{tab:survey_society}
    }
    \end{floatrow}
\end{figure}

% \begin{table}[h!]
% \centering
% \caption{A WSSSPE society?}
% \label{tab:survey_society}
% \begin{tabular}{|l|c|}
% \hline
% {\bf Answer} &
% {\bf Count} \\ \hline
% Yes &
% 24 \\
% No &
% 3 \\
% Maybe &
% 18 \\
% Total &
% 45 \\
% \hline
% \end{tabular}
% \end{table}
%
% \begin{figure}[h]
% \includegraphics[width=0.4\textwidth]{figures/SurveyFig5rev}
% \caption{Would you be interested in joining a professional society focused around the topics of WSSSPE?
% \label{fig:SFig5}}
% \end{figure}

\noindent \textbf{7. Will you be part of a working group  with colleagues going forward  on a topic addressed at WSSSPE, and if so, which one?}

\begin{figure}[h!]
    \CenterFloatBoxes
    \centering
    \begin{floatrow}
    \ffigbox[\FBwidth]{%
        \includegraphics[width=0.35\textwidth]{figures/SurveyFig6rev}%
    }{%
        \captionsetup{width=\linewidth}
        \caption{Will you be part of a working group  with colleagues going
        forward  on a topic addressed at WSSSPE?
        \label{fig:SFig6}}%
    }
    ~
    \killfloatstyle\capbtabbox[\linewidth]{%
    \rowcolors{1}{}{lightgray}
    \begin{tabular}{@{}ll@{}}
    \toprule
    Answer & Count \\
    \midrule
    Yes & 32 \\
    No & 4 \\
    Maybe & 9 \\
    Total & 45 \\
    \bottomrule
    \end{tabular}
    }{%
        \caption{Continuing working groups?}%
        \label{tab:survey_continuing_wgs}
    }
    \end{floatrow}
\end{figure}

% \begin{table}[h!]
% \centering
% \caption{Continuing working groups?}
% \label{tab:survey_continuing_wgs}
% \begin{tabular}{@{}ll@{}}
% \toprule
% Answer & Count \\
% \midrule
% Yes & 32 \\
% No & 4 \\
% Maybe & 9 \\
% Total & 45 \\
% \bottomrule
% \end{tabular}
% \end{table}

% \begin{figure}[h]
% \includegraphics[width=0.4\textwidth]{figures/SurveyFig6rev}
% \caption{Will you be part of a working group  with colleagues going forward  on a topic addressed at WSSSPE?
% \label{fig:SFig6}}
% \end{figure}

\noindent \textbf{8. Working Group Name}

@@

\noindent \textbf{9. Do you have any other comments or suggestions or ideas?}
